Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-07 article.Rmd
Hardcoded Kantrowitz error rate

```{r}
# Hardcode the error rate for now. This value is based on running the code above
# locally.
kantrowitz_error_rate <- 0
```

@@

The Solution:

The possibilities for encoding gender from names depends on two things. First, it depends on having a suitable (and suitably large) data set for the time period and region under study. Unsurprisingly such data sets are almost always gathered in the first instance by states, though the compilation and digitization may be undertaken by scholarly researchers. Second, it depends on a suitable algorithms for estimating the proportion of male and female names for a given year, or range of years since often a person cannot be associated with an exact date. It is important that the algorithm take into account any biases in the data to make correct predictions.

Data:

>>>>

```{r}
# Hardcode the error rate for now. This value is based on running the code above
# locally.
kantrowitz_error_rate <- 0.2325766
```

@@

To that end we have created the [Gender](https://github.com/ropensci/gender) package for R which contains the , and an associated [genderdata](https://github.com/lmullen/gender-data-pkg) package which contains various historical datasets.

The possibilities for encoding gender from names depends on two things. First, it depends on having a suitable (and suitably large) dataset for the time period and region under study. Unsurprisingly such datasets are almost always gathered in the first instance by states, though the compilation and digitization may be undertaken by scholarly researchers. Second, it depends on a suitable algorithm for estimating the proportion of male and female names for a given year, or range of years since often a person cannot be associated with an exact date. It is especially important that the algorithm take into account any biases in the data to make correct predictions.
